Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex
Normalize Table and Figure references

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
We conceptualized cuts as events with information on the depicted environment
that require viewers to re-orient themselves within the movie environment by
switching to a new perspective within the same setting, or to a position in an
entirely different setting.
% AV regressors/events
We assigned each cut to one of five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).
% irrespective of visual content
Note that this categorization is not necessarily evident from the visual content
of the first movie frame after a cut.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
and their spatial layout at the beginning of a movie.
% cut to recurrent scene
On revisiting an already established setting later in the movie, the field sizes
of movie shots tend to decrease (\texttt{vse\_old}), and shots tend to
more often depict people talking to each other, or objects that are relevant to
the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
mercado2011filmmakers}.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro

@@

    % negative control see Table \ref{tab:ao-events}.

@@

% AD annotation
For the analysis of the audio-description stimulus, we extended a publicly available annotation
of its speech content \citep{hausler2021studyforrest} by classifying
concrete and countable nouns that the narrator uses to describe the movie's absent visual content.
% annotation procedure
An initial annotation was performed by one individual,
% corrections
and minor corrections were applied after comparing with a second categorization
done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, their inclusion criteria, and examples
can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another category in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (see Table
\ref{tab:ao-events}). These event categories were then used to model hemodynamic
responses.

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Categories and rules to categorize the nouns spoken by
        the audio-description's narrator.
        Examples are given in English.
        Some of these initial 18 noun categories were pooled resulting in 11
        event categories that served as basis to build the regressors of the
        GLM
        (cf. Table \ref{tab:ao-events}).
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lp{61mm}p{61mm}}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
\texttt{body} & trunk of the body; possibly clothed & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
\texttt{bodypart} & limbs & arm, finger, leg, toe
\tabularnewline
\texttt{face} & face or parts of it & face, ear, nose, mouth
\tabularnewline
\texttt{female} & female person & nurse, mother, woman
\tabularnewline
\texttt{females} & female persons & women
\tabularnewline
\texttt{fname} & female name & Jenny
\tabularnewline
\texttt{furniture} & movable furniture (insides \& outsides) & bench, bed, table, chair
\tabularnewline
\texttt{geo} & immobile landmarks & building, tree, street, alley, meadow, cornfield
\tabularnewline
\texttt{geo-room} & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
\texttt{head} & non-face parts of the head; worn headgear & head, hair, ear, neck;
helmet
\tabularnewline
\texttt{male} & male person & man, father, soldier
\tabularnewline
\texttt{males} & male persons & boys, opponents
\tabularnewline
\texttt{mname} & male name & Bubba, Kennedy
\tabularnewline
\texttt{object} & countable entity with firm boundaries & telephone, car
\tabularnewline
\texttt{objects} & countable entities & wheels, plants
\tabularnewline
\texttt{persons} & concrete persons of unknown sex & hippies, patients
\tabularnewline
\texttt{setting\_new} & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
\texttt{setting\_rec} & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

    see Table\ref{tab:descr-nouns-rules}) were pooled

@@

    % Table \ref{tab:av-events}.

@@

% we checked correlations
Given the unknown confound structure of the naturalistic stimuli we inspected
% correlations within stimuli and across stimuli
the correlation of regressors across the eight segments of each stimulus and
also across both stimuli (Figure \ref{fig:reg-corr}).
% correlations within each stimulus
The computed Pearson correlation coefficients show only minor correlations of
feature regressors for the same stimulus.
% (highest) correlations across stimuli
Maximum correlations are found for auditory low-level confounds across stimuli
(\texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
\texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77),
% no surprise
which is to be expected, as the audio-description contains the audio track of
the movie plus the additional narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
Given that all planned voxel-wise general linear models (GLM) exclusively involve
regressors from one of the naturalistic stimuli, the observed correlation
pattern does not indicate problematic confounds of nuissance variables and
regressors of interest.

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of modeled time series used as regressors in
        the GLM analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table
        \ref{tab:av-events}).
        Values are rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square volume and between their left-right difference in
        volume yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
      }
\label{fig:reg-corr}
\end{figure*}

% AV design matrix
For the subsequent first level GLM analysis of the movie stimulus, the modeled
hemodynamic responses related to all movie cuts (including \texttt{no\_cut}) and
six low-level perceptual confounds were included as regressors in the design
matrix.
% AD regressors in AV AD design matrix
For the first level analysis of the audio-description stimulus, the modeled
hemodynamic responses related to all noun categories and the two low-level
perceptual confounds were included.
% AD regressors in AV
To create a contrasts of cross-modal control in the analysis of the movie
stimulus, we also implemented the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
To create contrasts of cross-modal negative control in the analysis of the
audio-description stimulus, we also implemented the movie cut-related regressors
(excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was chosen for a event category in a segment,
if that segment did not contain an event of the category (e.g. no event of
\texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also included.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

% similar to previous studies
On the first level, we created GLM contrasts based on annotated stimulus
features embedded in the in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of non-spatial information
differently in five $t$-contrasts for the movie stimulus (see Table
\ref{tab:av-contrasts}) and eight $t$-contrasts for the audio-description stimulus (see Table
\ref{tab:ao-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA but chose one contrast to be the ``primary contrast'' for
later detailed inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well the average of events within
categories represented spatial information and non-spatial information
respectively (cf. section \ref{rationale}), and b) the amount of available data.
% AV: primary contrast
In the primary contrast of the movie stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vse\_new}) to cuts merely switching the camera
position within a setting that was already established earlier in the movie
(\texttt{vpe\_old}).
% why
We assumed that the category \texttt{vse\_new} on average comprised the most
movie frames depicting a landscape or the geometry of a setting, and the
category \texttt{vpe\_old} the most frames depicting persons, faces, or objects
[(cf.  rationale to categorize the cuts in section \ref{rationale})].
% AD: primary contrast
In the primary contrast of the audio-description stimulus, we contrasted buildings and
landmarks (\texttt{geo}), and rooms and geometry-defining objects
(\texttt{geo-room}) with not just nouns referring to a person's head or face
(\texttt{fahead}, N=83; e.g.  ``eyes'', ``face'', or ``head'') but also all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture} to get more events per stimulus segment.\todo{ouff}
% why furniture was not used
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) categories comprise nouns that could count as a member of another category
(e.g. ``[a] physician''; section \ref{rationale}), and
% richness of verbal description vs. picture
b) nouns that only vaguely describe a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures].
% and c) the narrator is often lacking behind a short dialogue or a change of
% the soundscape that might already indicate a change of settings.

% control contrasts
Finally, we created several $t$-contrasts as negative controls for both stimuli
(see Tables \ref{tab:av-contrasts} and \ref{tab:ao-contrasts}).
% AV: no cut > cut
For the movie stimulus, four contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
nouns spoken by the narrator.
% AD stimulus
For the audio-description stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts.

@@

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the audio-only
    stimulus.
    Contrast 1-8 aim to isolate the PPA.
    \texttt{non-spatial categories} refers to the categories
    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
    Contrasts 9-13 serve as negative control contrasts at the moments of movie
    cuts (see Table \ref{tab:av-contrasts}).}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > non-spatial categories & PPA \tabularnewline
2 & geo, groom, se\_new > non-spatial categories & PPA \tabularnewline
3 & groom, se\_new, se\_old > non-spatial  & PPA \tabularnewline
4 & geo > non-spatial categories & PPA \tabularnewline
5 & groom > non-spatial categories & PPA \tabularnewline
6 & se\_new > non-spatial categories & PPA \tabularnewline
7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
8 & se\_new > se\_old > non-spatial categories & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

@@

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts within a recurring setting (\texttt{vse\_new >
vpe\_old}) yielded three significant clusters (see Table
\ref{tab:res-av-group1}, Figure \ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex.

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas: 3 different most prob. locations depen. on
voxel}
% precuneus
Two additional homologous clusters are apparent in the ventral precuneus
extending into the retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual participants to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Further, we hypothesized that an exclusively auditory stimulus could localize
the PPA in individual participants and thus possibly substitute a classic visual
localizer experiment.
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
The visual localizer yielded bilateral parahippocampal clusters in 12 of 14
participants and an unilateral right clusters in two participants (cf. Table 3 in
\citep{sengupta2016extension}).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $t$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts, and
titrating\todo{??} the $t$-threshold in the range of [2, 3] in until we found an
isolated cluster (cf. Table 3 in that matched the expected anatomical location
based on literature \citep{epstein1998ppa}.

>>>>

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
We conceptualized cuts as events with information on the depicted environment
that require viewers to re-orient themselves within the movie environment by
switching to a new perspective within the same setting, or to a position in an
entirely different setting.
% AV regressors/events
We assigned each cut to one of five categories (Tab.~\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).
% irrespective of visual content
Note that this categorization is not necessarily evident from the visual content
of the first movie frame after a cut.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
and their spatial layout at the beginning of a movie.
% cut to recurrent scene
On revisiting an already established setting later in the movie, the field sizes
of movie shots tend to decrease (\texttt{vse\_old}), and shots tend to
more often depict people talking to each other, or objects that are relevant to
the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
mercado2011filmmakers}.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro

@@

    % negative control Tab.~\ref{tab:ao-events}.

@@

% AD annotation
For the analysis of the audio-description stimulus, we extended a publicly available annotation
of its speech content \citep{hausler2021studyforrest} by classifying
concrete and countable nouns that the narrator uses to describe the movie's absent visual content.
% annotation procedure
An initial annotation was performed by one individual,
% corrections
and minor corrections were applied after comparing with a second categorization
done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, their inclusion criteria, and examples
can be seen in Table~\ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another category in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (Tab.~\ref{tab:ao-events}).
These event categories were then used to model hemodynamic
responses.

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Categories and rules to categorize the nouns spoken by
        the audio-description's narrator.
        Examples are given in English.
        Some of these initial 18 noun categories were pooled resulting in 11
        event categories that served as basis to build the regressors of the
        GLM
        (Tab.~\ref{tab:ao-events}).
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lp{61mm}p{61mm}}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
\texttt{body} & trunk of the body; possibly clothed & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
\texttt{bodypart} & limbs & arm, finger, leg, toe
\tabularnewline
\texttt{face} & face or parts of it & face, ear, nose, mouth
\tabularnewline
\texttt{female} & female person & nurse, mother, woman
\tabularnewline
\texttt{females} & female persons & women
\tabularnewline
\texttt{fname} & female name & Jenny
\tabularnewline
\texttt{furniture} & movable furniture (insides \& outsides) & bench, bed, table, chair
\tabularnewline
\texttt{geo} & immobile landmarks & building, tree, street, alley, meadow, cornfield
\tabularnewline
\texttt{geo-room} & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
\texttt{head} & non-face parts of the head; worn headgear & head, hair, ear, neck;
helmet
\tabularnewline
\texttt{male} & male person & man, father, soldier
\tabularnewline
\texttt{males} & male persons & boys, opponents
\tabularnewline
\texttt{mname} & male name & Bubba, Kennedy
\tabularnewline
\texttt{object} & countable entity with firm boundaries & telephone, car
\tabularnewline
\texttt{objects} & countable entities & wheels, plants
\tabularnewline
\texttt{persons} & concrete persons of unknown sex & hippies, patients
\tabularnewline
\texttt{setting\_new} & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
\texttt{setting\_rec} & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

    Tab.~\ref{tab:descr-nouns-rules}) were pooled

@@

    % Tab.~\ref{tab:av-events}.

@@

% we checked correlations
Given the unknown confound structure of the naturalistic stimuli we inspected
% correlations within stimuli and across stimuli
the correlation of regressors across the eight segments of each stimulus and
also across both stimuli (Fig.~\ref{fig:reg-corr}).
% correlations within each stimulus
The computed Pearson correlation coefficients show only minor correlations of
feature regressors for the same stimulus.
% (highest) correlations across stimuli
Maximum correlations are found for auditory low-level confounds across stimuli
(\texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
\texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77),
% no surprise
which is to be expected, as the audio-description contains the audio track of
the movie plus the additional narrator (Fig. \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
Given that all planned voxel-wise general linear models (GLM) exclusively involve
regressors from one of the naturalistic stimuli, the observed correlation
pattern does not indicate problematic confounds of nuissance variables and
regressors of interest.

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of modeled time series used as regressors in
        the GLM analysis of the
        audio-description (blue; Tab.~\ref{tab:ao-events} for a
        description) and audio-visual movie (red; Tab.~\ref{tab:av-events}).
        Values are rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square volume and between their left-right difference in
        volume yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
      }
\label{fig:reg-corr}
\end{figure*}

% AV design matrix
For the subsequent first level GLM analysis of the movie stimulus, the modeled
hemodynamic responses related to all movie cuts (including \texttt{no\_cut}) and
six low-level perceptual confounds were included as regressors in the design
matrix.
% AD regressors in AV AD design matrix
For the first level analysis of the audio-description stimulus, the modeled
hemodynamic responses related to all noun categories and the two low-level
perceptual confounds were included.
% AD regressors in AV
To create a contrasts of cross-modal control in the analysis of the movie
stimulus, we also implemented the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
To create contrasts of cross-modal negative control in the analysis of the
audio-description stimulus, we also implemented the movie cut-related regressors
(excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was chosen for a event category in a segment,
if that segment did not contain an event of the category (e.g. no event of
\texttt{vpe\_old} in segment 3; Tab.~\ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also included.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

% similar to previous studies
On the first level, we created GLM contrasts based on annotated stimulus
features embedded in the in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of non-spatial information
differently in five $t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts})
and eight $t$-contrasts for the audio-description stimulus (Tab.~\ref{tab:ao-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA but chose one contrast to be the ``primary contrast'' for
later detailed inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well the average of events within
categories represented spatial information and non-spatial information
respectively (cf. section \ref{rationale}), and b) the amount of available data.
% AV: primary contrast
In the primary contrast of the movie stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vse\_new}) to cuts merely switching the camera
position within a setting that was already established earlier in the movie
(\texttt{vpe\_old}).
% why
We assumed that the category \texttt{vse\_new} on average comprised the most
movie frames depicting a landscape or the geometry of a setting, and the
category \texttt{vpe\_old} the most frames depicting persons, faces, or objects
[(cf.  rationale to categorize the cuts in section \ref{rationale})].
% AD: primary contrast
In the primary contrast of the audio-description stimulus, we contrasted buildings and
landmarks (\texttt{geo}), and rooms and geometry-defining objects
(\texttt{geo-room}) with not just nouns referring to a person's head or face
(\texttt{fahead}, N=83; e.g.  ``eyes'', ``face'', or ``head'') but also all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture} to get more events per stimulus segment.\todo{ouff}
% why furniture was not used
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) categories comprise nouns that could count as a member of another category
(e.g. ``[a] physician''; section \ref{rationale}), and
% richness of verbal description vs. picture
b) nouns that only vaguely describe a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures].
% and c) the narrator is often lacking behind a short dialogue or a change of
% the soundscape that might already indicate a change of settings.

% control contrasts
Finally, we created several $t$-contrasts as negative controls for both stimuli
(Tab.~\ref{tab:av-contrasts} and Tab.~\ref{tab:ao-contrasts}).
% AV: no cut > cut
For the movie stimulus, four contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
nouns spoken by the narrator.
% AD stimulus
For the audio-description stimulus, we created five $t$-contrasts
(Tab.~\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts.

@@

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the audio-only
    stimulus.
    Contrast 1-8 aim to isolate the PPA.
    \texttt{non-spatial categories} refers to the categories
    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
    Contrasts 9-13 serve as negative control contrasts at the moments of movie
    cuts (Tab.~\ref{tab:av-contrasts}).}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > non-spatial categories & PPA \tabularnewline
2 & geo, groom, se\_new > non-spatial categories & PPA \tabularnewline
3 & groom, se\_new, se\_old > non-spatial  & PPA \tabularnewline
4 & geo > non-spatial categories & PPA \tabularnewline
5 & groom > non-spatial categories & PPA \tabularnewline
6 & se\_new > non-spatial categories & PPA \tabularnewline
7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
8 & se\_new > se\_old > non-spatial categories & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

@@

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts within a recurring setting (\texttt{vse\_new >
vpe\_old}) yielded three significant clusters (Tab.~\ref{tab:res-av-group1},
Fig.~\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex.

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters
(Tab.~\ref{tab:res-ao-group1}, Fig.~\ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas: 3 different most prob. locations depen. on
voxel}
% precuneus
Two additional homologous clusters are apparent in the ventral precuneus
extending into the retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual participants to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Further, we hypothesized that an exclusively auditory stimulus could localize
the PPA in individual participants and thus possibly substitute a classic visual
localizer experiment.
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
The visual localizer yielded bilateral parahippocampal clusters in 12 of 14
participants and an unilateral right clusters in two participants (Tab.~3 in
\citep{sengupta2016extension}).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $t$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts, and
titrating\todo{??} the $t$-threshold in the range of [2, 3] in until we found an
isolated cluster (Tab.~3 in that matched the expected anatomical location
based on literature \citep{epstein1998ppa}.

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all participants.
% subject space -> NeuroVault
Results of the analyses that were performed in participant-space can be found in the
accompanying dataset (Z>2.3, p<.05 cluster-corrected).
% here report in group space
For better comparisons of participants, we here report results from the analyses
performed in group space (Z>3.4, p<.05 cluster-corrected).
% ref to figure
Figure~\ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary movie
and audio-description $t$-contrast, and the outline of overlapped, individual PPAs
co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts voxels of
significant clusters in almost all participants.
